Simulating Ultra High-Dimensional Multivariate Data Using the bigsimr R Package

### 2020-06-19 index.Rmd
add serve_book() convenience comment

```{r LoadLib, echo = FALSE, eval = TRUE, message=FALSE, warning=FALSE, results = "hide"}
library(ggplot2)
library(tidyverse)
library(knitr)
library(dplyr)
## devtools::install_github( "adknudson/bigsimr", ref = 'develop')
set.seed(06082020)
```

>>>>

```{r LoadLib, echo = FALSE, eval = TRUE, message=FALSE, warning=FALSE, results = "hide"}
library(ggplot2)
library(tidyverse)
library(knitr)
library(dplyr)
## devtools::install_github( "adknudson/bigsimr", ref = 'develop')
## bookdown::serve_book()
set.seed(06082020)
```
